---
title: "Reproducible Research - Assessment 1"
author: "JSS"
date: "July 25, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Goals for This Assignment
1. Load and preprocess the data
2. Make a histogram of the total number of steps taken each day and calculate and report the mean and median of the total number of steps taken per day
3. Make a time series plot to determin Which 5-minute interval, on average across all the days, contains the maximum number of steps
4. Calculate and report the total number of missing values in the dataset. Devise a strategy for filling in all of the missing values in the dataset.
5. Create a new dataset with the missing data filled in. Make a histogram of the total number of steps taken each day and Calculate and report the mean and     median total number of steps taken per day.
6. Look for pattern differences in weekends vs weekdays.

## Step 1: Load and preprocess the data
```{r
#Create data frame = df
df <- read.table("activity.csv",
                header=TRUE,
                sep=",",
                stringsAsFactors = FALSE,
                colClasses = c("numeric","Date","numeric")}

```
## Step 2A - Make a histogram 
```{r 
TotalStepsByDay <- aggregate(df$steps,list(date=df$date),sum,na.rm=TRUE)
        xAxisBreakdown = seq(from=0,to=25000,by=2000) 
        hist(TotalStepsByDay$x,
         breaks = xAxisBreakdown,
         main="Frequency of Total Steps per Day",
                col="blue",
                xlab="Steps",
                ylab="Days",
                xaxt="n")
        axis(side=1,at=xAxisBreakdown,labels=xAxisBreakdown)}

```

